\Large \bf Apropos Replacement : Development of a full text search tool for man pages

### 2012-02-29 apropos_replacement.tex
Remove unnecessary text
Some preformance stats

\section{Limitations of Conventional \textit{apropos}}
In this section results of some sample query searches from
the classical version of \textit{apropos} are shown and their shortcomings are
analyzed. \\

@@

Similarly along with the inverted index, a dictionary of the keywords frequently
occurring in the corpus of man pages is also built and used to support
spelling suggestion.
\end{description}
\begin{description}
\item[Bookkeeping of man page metadata] \hfill \\
In this implementation, additional metadata related to the man pages, for example
an MD5 hash, the device id, inode number and modification time
of the man page files are kept.
This allows fast incremental update of the index as new man pages are installed or the old ones are updated. \\

@@

\pagebreak
\section{Results}
{\bf Listing \ref{newUser}}, {\bf \ref{makeDirectory}}, and {\bf \ref{signal} } show results of some of the sample queries on new \textit{apropos}
to demonstrate how it performs as compared to the traditional version.
\endnote{Although the new \textit{apropos} by default returns 10
results for a query but in the listings the output has been
snipped to save space
} \\

In \textbf{Figure 1} the spell corrector can be seen in action along with the web
interface that was developed using \textit{apropos-utils}. \\

@@

\begin{description}
\item[Using external storage] \hfill \\
A new feature is under development in \textit{Sqlite}, to support external
storage option in FTS databases. This option would allow building the FTS
index without actually storing any content in the database itself (except for
the data required to maintain the indexes). This will save bulk of the disk
space currently required by \textit{apropos} database. The disk space thus
saved might also allow for experiments with ranking algorithms which require
storing additional metadata on the disk.
\end{description}

\section{Availability}
The code for this project has been imported into the NetBSD source tree and
being maintained there. Experimental work is still being done in the \textit
{github} repository of the project. It can be obtained from:\newline

@@

\pagebreak
\section{Acknowledgement}
This project has been developed as part of \emph{Google Summer of Code 2011}
[17], thanks to \textbf{Google} for sponsoring it. Special thanks to
\textbf{Kristaps Dzonsons} who is the developer of the \textit{mdocml} [18]
project, he also helped by pointing out several issues in the parsing related
code. Thanks to \textbf{David Young} who was involved with
this project closely and offered useful guidance and encouragement throughout. A
special thanks goes to \textbf{Thomas Klausner} who helped in writing and
reviewing the man pages for this project. Thanks to \textbf{Petra Zeidler} for
administering the GSoC program for \textit{The NetBSD Foundation}. \\

>>>>

\section{Limitations of Conventional \textit{apropos}}

@@

Similarly along with the inverted index, a dictionary of the keywords frequently
occurring in the corpus of man pages is also built and used to support
spelling suggestion.
\end{description}
\begin{description}
\item[Bookkeeping of man page metadata] \hfill \\
In this implementation, additional metadata related to the man pages, for example
an MD5 hash, the device id, inode number and modification time
of the man page files are kept in the database.
This allows fast incremental update of the index as new man pages are installed or the old ones are updated. \\

@@

\pagebreak
\section{Results}
\subsection{Performance of apropos}
{\bf Listing \ref{newUser}}, {\bf \ref{makeDirectory}}, and {\bf \ref{signal} } show results of some of the sample queries on new \textit{apropos}
to demonstrate how it performs as compared to the traditional version.
\endnote{Although the new \textit{apropos} by default returns 10
results for a query but in the listings the output has been
snipped to save space
}
In \textbf{Figure 1}, the spell corrector can be seen in action along with the web
interface that was developed using \textit{apropos-utils}. \\

\subsection{Performance of makemandb} 
On a modern desktop hardware, \textit{makemandb} takes about 25 seconds
to index 4000 man pages, and the size of this index is $15$ MB. When 
the number of man pages is increased to 6100 by including some packages from
\textit{pkgsrc}, the time taken by \textit{makemandb} grows to about 50 seconds
and the size of the database index grows to $27$ MB. \\

@@

\begin{description}
\item[Using external storage] \hfill \\
A new feature is under development in \textit{Sqlite}, to support external
storage option in FTS databases. This option would allow building the FTS
index without actually storing any content in the database itself (except for
the data required to maintain the indexes). This will save bulk of the disk
space currently required by \textit{apropos} database. The disk space thus
saved might also allow for experiments with ranking algorithms which require
storing additional metadata on the disk.
\end{description}
\pagebreak
\section{Availability}
The code for this project has been imported into the NetBSD source tree and
being maintained there. Experimental work is still being done in the \textit
{github} repository of the project. It can be obtained from:\newline

@@

\section{Acknowledgement}
This project has been developed as part of \emph{Google Summer of Code 2011}
[17], thanks to \textbf{Google} for sponsoring it. Special thanks to
\textbf{Kristaps Dzonsons} who is the developer of the \textit{mdocml} [18]
project, he also helped by pointing out several issues in the parsing related
code. Thanks to \textbf{David Young} who was involved with
this project closely and offered useful guidance and encouragement throughout. A
special thanks goes to \textbf{Thomas Klausner} who helped in writing and
reviewing the man pages for this project. Thanks to \textbf{Petra Zeidler} for
administering the GSoC program for \textit{The NetBSD Foundation}. \\
